---
title: "Testing metrics for crystallographic order"
author: "Bryan Shirley and Emilia Jarochowska"
date: "2024-05-15"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages(setdiff(c("ggplot2", "ggpubr", "knitr", "osfr"), rownames(installed.packages())))  
library(ggplot2)
library(ggpubr)
library(knitr)
```

The data files are downloaded from Open Science Framework. This needs to be done only once.
```{r downloading the data, eval = T}
# Set eval = F to prevent this code chunk from downloading data every time
source("../get_data_from_osf.R")
get_data_from_osf(link = "https://osf.io/vnq6s/")
```

Once a copy of the dataset is on the local computer, it can be imported into R:
```{r Read into R}
Data = read.csv(file = "Figure_3_and_4.csv",
                header = T, 
                sep=';')
Data$Taxa <- factor(Data$Taxa, 
                    levels = c("Pro.muelleri", 
                               "Pan.equicostatus", 
                               "B. cf. aculeatus", 
                               "W. excavata", 
                               "T. gracilis", 
                               "Palmatolepis sp."))
```


```{r Setting up the box plots, echo=FALSE}
color_scale <- c(
                 "#a36b2bff", # Pro.muelleri
                 "#bf9e66ff", # Pan.equicostatus
                 "#aecec5ff", # B. cf. aculeatus
                 "#2686a0ff", # W. excavata
                 "#dcd1a2ff", # T. gracilis
                 "#cad5c1ff") # Palmatolepis sp.
                 

p1 = ggplot(data = Data, aes(x=Taxa, y=T.index,fill=Taxa)) + 
  geom_boxplot()+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=9))+
  ylab("Texture index")+
  scale_fill_manual(values=color_scale)

p2 = ggplot(data = Data, aes(x=Taxa, y=M.index,fill=Taxa)) + 
  geom_boxplot()+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=9))+
  ylab("M-index")+
  scale_fill_manual(values=color_scale)

p3 = ggplot(data = Data, aes(x=Taxa, y=pfT.index..C.,fill=Taxa)) + 
  geom_boxplot()+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=9))+
  ylab("pfT-index (C)")+
  scale_fill_manual(values=color_scale)

p4 = ggplot(data = Data, aes(x=Taxa, y=pfT.index..A.,fill=Taxa))+ 
  geom_boxplot()+
  theme_classic()+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=9),
        legend.position.inside = c(0.9, 0.05))+
  ylab("pfT-index (A)")+
  scale_fill_manual(name = "Taxon", 
                      labels = c(expression(italic("Pro. muelleri")),                 
                      expression(italic("Pan. equicostatus")),            
                      expression(italic("B.")~ "cf."~italic("aculeatus")),          
                      expression(italic("W. excavata")),           
                      expression(italic("T. gracilis")),            
                      expression(italic("Palmatolepis")~ "sp.")),
                     values = color_scale)+
  theme(legend.text=element_text(size=6))
```

## All the methods

Here we plot 3 methods of looking at the texture index of materials. First, we use the Texture Index (TI), followed by the misorientation index (M-index) and then the pole figure texture index  (pfT-index) for the A and C axis. 

```{r}
boxplots <- ggpubr::ggarrange(p1, p2,p3,p4,
                  labels = c("a", "b", "c","d"),
                  ncol = 2, nrow = 2)
boxplots
```


```{r, include=F}
ggsave(filename = "boxplots.pdf",
       plot = boxplots,
       width = 180,
       height = 130,
       units = "mm")
```

```{r scatter plots to compare the difference between the M-index and the T Index,echo=FALSE}
sc1= ggplot2::ggplot(Data, aes(y=M.index, x=T.index, color=Taxa, shape=Taxa)) + 
  geom_point(size=2) + 
  ylab(expression("M-index")) + 
  xlab(expression("T-index"))+
  theme_classic()+
  theme(legend.position = "none")+
  scale_colour_manual(values=color_scale)+
scale_shape_manual(values=c(4,15,16,17,18,25))+
  geom_point(size=1.5,stroke = 1.5)


sc2= ggplot2::ggplot(Data, aes(y=pfT.index..C., x=pfT.index..A., color=Taxa, shape=Taxa)) + 
  geom_point(size=2) + 
  ylab(expression("pfT-index(C)")) + 
  xlab(expression("pfT-index(A)"))+
  theme_classic()+
  geom_point(size=1.5,stroke = 1.5)+
  scale_color_manual(name = "Taxon", 
                      labels = c(expression(italic("Pro. muelleri")),                 
                      expression(italic("Pan. equicostatus")),            
                      expression(italic("B.")~ "cf."~italic("aculeatus")),          
                      expression(italic("W. excavata")),           
                      expression(italic("T. gracilis")),            
                      expression(italic("Palmatolepis")~ "sp.")),
                     values = color_scale)+
  scale_shape_manual(name = "Taxon",
                     labels = c(expression(italic("Pro. muelleri")),                 
                      expression(italic("Pan. equicostatus")),            
                      expression(italic("B.")~ "cf."~italic("aculeatus")),          
                      expression(italic("W. excavata")),           
                      expression(italic("T. gracilis")),            
                      expression(italic("Palmatolepis")~ "sp.")),
                     values=c(4,15,16,17,18,25))

```

## Big combi plot

A combination plot of the texture index comparison.

```{r comparing area vs indices, echo=FALSE}
TI_area <- ggplot2::ggplot(Data, aes(y=T.index, x=Area, color=Taxa, shape=Taxa)) + 
  geom_point(size=2,stroke = 1) + 
  ylab(expression("T-index")) + 
  xlab(expression("Area"))+
  theme_classic()+
  geom_smooth(method=lm,se=FALSE,show.legend=TRUE)+
  theme(legend.position = "none")+
  scale_colour_manual(values=color_scale)+
  scale_shape_manual(values=c(4,15,16,17,18,25))
  
MI_area<- ggplot2::ggplot(Data, aes(y=M.index, x=Area, color=Taxa, shape=Taxa)) + 
  geom_point(size=2,stroke = 1) + 
  ylab(expression("M-index")) + 
  xlab(expression("Area"))+
  theme_classic()+
  geom_smooth(method=lm,se=FALSE)+
  theme(legend.position = "none")+
  scale_colour_manual(values=color_scale)+ 
  scale_shape_manual(values=c(4,15,16,17,18,25))

```

```{r Composite plot used in Extended Data}
composite <- ggarrange(ggarrange(TI_area, MI_area, ncol = 2, labels = c("a", "b")),
          ggarrange(sc1, sc2, ncol = 2, labels = c("c", "d")),
          nrow = 2, 
          labels = "a")
composite
```

```{r, include=F}
ggsave(filename = "composite.png",
       plot = composite,
       dpi = 300,
       width = 9)
```

## Regression analysis

Using linear regression to explore the relationship between TI and area:

```{r Regression between TI and area, include = F}
source("overall_p.R")
source("regression.R")
Regression_results <- regression(unique(Data$Taxa))
```

```{r, echo=FALSE}
kable(x = Regression_results,
      row.names = F)
```

## Figure 3

```{r}
library(tidyverse)
hull_data <- 
  Data %>%
  group_by(Taxa) %>% 
  slice(chull(T.index, Area))

scatterplot <- ggplot(data = Data, aes(x=Area, y=T.index, shape = Taxa, color=Taxa, fill = Taxa))+
  scale_color_manual(values = color_scale) +
  scale_fill_manual(values = color_scale) +
  scale_shape_manual(values = c(4,15,16,17,18,25))+
  geom_polygon(data = hull_data,
               aes(fill = Taxa,
                   colour = Taxa),
               alpha = 0.1,
               show.legend = FALSE)+
  theme_bw()+
  geom_point()+
  ylab(expression("Texture index")) + 
  xlab(expression(paste("Area ", mu, "m"^2)))+
  theme(legend.position = "bottom")
```

Combined Fig. 3:

```{r}
Fig_3 <- ggpubr::ggarrange(p1, scatterplot,
                  labels = c("a", "b"),
                  ncol = 1, nrow = 2,
                  heights = c(1, 2))
```

```{r}
ggsave(filename = "Figure_3.pdf",
       plot = Fig_3,
       dpi = 300,
       width = 180,
       height = 170,
       units = "mm")
```


## Test for the equality of means for the T Index

```{r}
aggregate(T.index ~ Taxa, data=Data, mean)
```
```{r Kruskal-Wallis test}
kruskal.test(T.index ~ Taxa, 
             data = Data) 
```
```{r confidence level}
cl = 0.05/6
```


To apply the (conservative) Bonferroni correction, generate a table with pairwise confidence intervals for each taxon:

```{r}
Wilcox_corrected <- array(data = NA,
                          dim = c(6,6,2),
                          dimnames = list("Taxon" = levels(Data$Taxa), 
                                          "Taxon" = levels(Data$Taxa), 
                                          "Conf.Interval" = c("Lower", "Upper"))
                          )

for (i in levels(Data$Taxa)) {
  for (j in levels(Data$Taxa)) {
    if (i == j) {
      Wilcox_corrected[i,j,] <- c(NA,NA)
    }
    else {
      Wilcox_corrected[i,j,] <- wilcox.test(Data$T.index[which(Data$Taxa == i)],
                                         Data$T.index[which(Data$Taxa == j)], 
                                         conf.int=T, 
                                         conf.lev=cl)$conf.int
    }
  }
}
```

```{r}
write.table(Wilcox_corrected[i,j,1], 
            file = "Lower_CI.csv", 
            sep = ",",
            row.names = T,
            col.names = T)
```


And p-values for the same Bonferroni correction:

```{r}
Wilcox_pval <- matrix(data = NA,
                            nrow = length(levels(Data$Taxa)),
                            ncol = length(levels(Data$Taxa)),
                            dimnames = list("Taxon" = levels(Data$Taxa), "Taxon" = levels(Data$Taxa)))

for (i in levels(Data$Taxa)) {
  for (j in levels(Data$Taxa)) {
    if (i == j) {
      Wilcox_pval[i,j] <- NA
    }
    else {
      Wilcox_pval[i,j] <- wilcox.test(Data$T.index[which(Data$Taxa == i)],
                                         Data$T.index[which(Data$Taxa == j)], 
                                         conf.int=T, 
                                         conf.lev=cl)$p.value
    }
  }
}
```

Make a nice table:
```{r}
kable(x = Wilcox_pval,
      row.names = T)
```

