---
title: "Testing metrics for crystallographic order"
author: "Bryan Shirley and Emilia Jarochowska"
date: "2023-01-14"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages(setdiff(c("ggplot2", "ggpubr", "knitr", "osfr"), rownames(installed.packages())))  
library(ggplot2)
library(ggpubr)
library(knitr)
```

The data files are downloaded from Open Science Framework. 
```{r importing the data, include = F}
source("../get_data_from_osf.R")
get_data_from_osf(link = "https://osf.io/vnq6s/")
Data = read.csv("Data Files/TextureResults.csv",header = T, sep=';')
```

```{r Setting up the box plots, echo=FALSE}

p1 = ggplot(data = Data, aes(x=reorder(Taxa,T.index), y=T.index,fill=Taxa)) + 
  geom_boxplot()

p2 = ggplot(data = Data, aes(x=reorder(Taxa,T.index), y=M.index,fill=Taxa)) + 
  geom_boxplot()

p3 = ggplot(data = Data, aes(x=reorder(Taxa,T.index), y=pfT.index..C.,fill=Taxa
)) + geom_boxplot()

p4 = ggplot(data = Data, aes(x=reorder(Taxa,T.index), y=pfT.index..A.,fill=Taxa
)) + geom_boxplot()
```

```{r, echo=F}
color_scale <- c("#aecec5ff","#cad5c1ff","#bf9e66ff","#a36b2bff","#dcd1a2ff", "#2686a0ff")

  p1 = p1 +theme_classic()+theme(legend.position = "none",axis.text.x=element_blank(),axis.ticks.x=element_blank(),
                                 axis.title.x = element_blank(),axis.title.y = element_text(size=9))+
    ylab("T-index")+
    scale_fill_manual(values=color_scale)

  p2 = p2 +theme_classic()+theme(legend.position = "none",axis.text.x=element_blank(),
                                 axis.ticks.x=element_blank(),axis.title.x = element_blank(),axis.title.y = element_text(size=9))+
    ylab("M-index")+
    scale_fill_manual(values=color_scale)
  
  p3 = p3 + theme_classic()+theme(legend.position = "none",axis.text.x=element_blank(),
                                  axis.ticks.x=element_blank(),axis.title.x = element_blank(),axis.title.y = element_text(size=9))+
    ylab("pfT-index (C)")+
    scale_fill_manual(values=color_scale)
  
  p4 = p4 +theme_classic()+theme(legend.position = "none",axis.text.x=element_blank(),
                                 axis.ticks.x=element_blank(),axis.title.x = element_blank(),axis.title.y = element_text(size=9))+
    ylab("pfT-index (A)")+
    scale_fill_manual(values=color_scale)
```

## All the methods

Here we plot 3 methods of looking at the texture index of materials. First, we use the Texture Index (TI), followed by the misorientation index (M-index) and then the pole figure texture index  (pfT-index) for the A and C axis. 

```{r,echo=FALSE}
ggpubr::ggarrange(p1, p2,p3,p4,
                  labels = c("a", "b", "c","d"),
                  ncol = 2, nrow = 2)
```

```{r scatter plots to compare the difference between the M-index and the T Index,echo=FALSE}
sc1= ggplot2::ggplot(Data, aes(y=M.index, x=T.index, color=Taxa, shape=Taxa)) + 
  geom_point(size=2) + 
  ylab(expression("M-index")) + 
  xlab(expression("T-index"))+
  theme_classic()+
  scale_colour_manual(values=color_scale)+
scale_shape_manual(values=c(4,15,16,17,18,25))+
  geom_point(size=1.5,stroke = 1.5)


sc2= ggplot2::ggplot(Data, aes(y=pfT.index..C., x=pfT.index..A., color=Taxa, shape=Taxa)) + 
  geom_point(size=2) + 
  ylab(expression("pfT-index(C)")) + 
  xlab(expression("pfT-index(A)"))+
  theme_classic()+
  scale_colour_manual(values=color_scale)+
scale_shape_manual(values=c(4,15,16,17,18,25))+
  geom_point(size=1.5,stroke = 1.5)

```

## Big combi plot

This is just a combination plot of the above data.

```{r playing with plots,echo=FALSE}
ggarrange(sc1,                                            
          ggarrange(p1,p2 , ncol = 2, labels = c("b", "c")),
          ggarrange(p3,p4 , ncol = 2, labels = c("d", "e")),
          nrow =3, 
          labels = "a"   ,      
          heights = c(1.8, 1,1)
) 
```

```{r comparing area vs indices, echo=FALSE}
TI_area <- ggplot2::ggplot(Data, aes(y=T.index, x=Area, color=Taxa, shape=Taxa)) + 
  geom_point(size=2,stroke = 1) + 
  ylab(expression("T-index")) + 
  xlab(expression("Area"))+
  theme_classic()+
  geom_smooth(method=lm,se=FALSE,show.legend=TRUE)+
  theme(legend.position = "none")+
  scale_colour_manual(values=color_scale)+
  scale_shape_manual(values=c(4,15,16,17,18,25))
  
MI_area<- ggplot2::ggplot(Data, aes(y=M.index, x=Area, color=Taxa, shape=Taxa)) + 
  geom_point(size=2,stroke = 1) + 
  ylab(expression("M-index")) + 
  xlab(expression("Area"))+
  theme_classic()+
  geom_smooth(method=lm,se=FALSE)+
  theme(legend.position = "none")+
  scale_colour_manual(values=color_scale)+ 
  scale_shape_manual(values=c(4,15,16,17,18,25))

```
## Composite plot used in Extended Data

```{r Composite plot used in Extended Data, echo=F}
composite <- ggarrange(ggarrange(TI_area, MI_area, ncol = 2, labels = c("a", "b")),
          ggarrange(sc1, sc2, ncol = 2, labels = c("c", "d")),
          nrow = 2, 
          labels = "a")
composite
```

```{r, include=F}
ggsave(filename = "composite.png",
       plot = composite,
       dpi = 300,
       width = 9)
```

## Regression analysis

Using linear regression to explore the relationship between TI and area:

```{r Regression between TI and area, include = F}
source("overall_p.R")
source("regression.R")
Regression_results <- regression(unique(Data$Taxa))
```

```{r, echo=FALSE}
kable(x = Regression_results,
      row.names = F)
```